---
title: "Assignment7 Network"
author: "Qian Yi"
date: "11/4/2020"
output: html_document
---

```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
library(tidyverse)
library(tidyxl)
library(janitor)
library(igraph)
library(tidygraph)
library(circlize)
library(dplyr)
library(magrittr)

```

```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
migrations=readxl::read_xls('/Users/qianyi/Desktop/Data/State_to_State_Migrations_Table_2018.xls', skip=4)
```

```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# drop foot notes (bottom 9 rows)
migrations=migrations[1:(dim(migrations)[1]-9),] 

# drop rows with all NA values 
migrations=migrations %>% remove_empty("rows")

# rename 
migrations=migrations %>% rename("current_residence"="Current residence in...1")

# remove duplicate columns (state information)
migrations <- migrations[, -grep("Current+\\s+residence+\\s+in", colnames(migrations))]

```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# New York, Texas, Maryland, California 
state4=cbind(migrations[, "current_residence"], migrations[, which(migrations[1,]=='New York')], migrations[, which(migrations[1,]=='Texas')], migrations[, which(migrations[1,]=='Maryland')], migrations[, which(migrations[1,]=='California')])
names(state4)[2:5]=c('New York', 'Texas', 'Maryland', 'California')

# drop the top 2 rows and NA value rows 
state4=state4[4:(dim(state4)[1]),]
state4=state4 %>% drop_na()

# remove Puerto Rico
state4=state4[which(state4["current_residence"]!='Puerto Rico'),]
```

```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# New York 
nydata=state4 %>% select("current_residence", "New York") 
nydata['New York'] %<>% mutate_if(is.character,as.numeric)
nydata=nydata[order(-nydata['New York']),] %>% top_n(10) 
source=c('New York')
df1=cbind(source,nydata)
df1=df1 %>% rename(c('target'='current_residence', 'count'='New York'))

# Texas
txdata=state4 %>% select("current_residence", "Texas") 
txdata['Texas'] %<>% mutate_if(is.character,as.numeric)
txdata=txdata[order(-txdata['Texas']),] %>% top_n(10) 
source=c('Texas')
df2=cbind(source,txdata)
df2=df2 %>% rename(c('target'='current_residence', 'count'='Texas'))


# Maryland
mddata=state4 %>% select("current_residence", "Maryland") 
mddata['Maryland'] %<>% mutate_if(is.character,as.numeric)
mddata=mddata[order(-mddata['Maryland']),] %>% top_n(10) 
source=c('Maryland')
df3=cbind(source,mddata)
df3=df3 %>% rename(c('target'='current_residence', 'count'='Maryland'))

# California 
cadata=state4 %>% select("current_residence", "California") 
cadata['California'] %<>% mutate_if(is.character,as.numeric)
cadata=cadata[order(-cadata['California']),] %>% top_n(10) 
source=c('California')
df4=cbind(source,cadata)
df4=df4 %>% rename(c('target'='current_residence', 'count'='California'))


# combine the dataset together 
network=rbind(df1,df2,df3,df4)

# save the data 
#write.csv(network, "network.csv")

# show the some rows of the dataset 
#head(network,10)
```


```{r, fig.height = 20, fig.width = 15, echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
# set grid color

chordDiagram(network, annotationTrack = "grid", 
    preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(network))))))
circos.track(track.index = 1, panel.fun = function(x, y) {
    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
        facing = "clockwise", niceFacing = TRUE,  adj = c(0, 0.8),cex=2)
}, bg.border = NA) # here set bg.border to NA is important

title("Top 10 Migration Destinations of NY, TX, MD and CA", cex.main = 2)

```

#### Discussion of the Visualization 

* As the graph shown above, the top 10 migration destinations of New York, Texas, Maryland and California were displayed. 

* It seems that Florida and Arizona were  popular places for people to migrate, maybe due to the warm weather. 

* It is also obvious that: Compared with Maryland, the other 3 states (California, Texas and New York) had more people to move away during the previous year. 













