---
title: "Visualization A6 Geospatial Graphs"
author: "Qian Yi"
date: "12/8/2020"
output: html_document
---

```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(janitor)
library(tidyverse)
library(ggplot2)
library(sf)
library(spData, warn.conflicts = F, quietly = T)
library(maps, warn.conflicts = F, quietly = T)
library(viridis)
library(ggpubr)
```



```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# Task 1 data cleaning--R 
# read the dataset
countypres=read.csv('/Users/qianyi/Desktop/Data/countypres_2000-2016.csv')
unemployment=read_excel('/Users/qianyi/Desktop/Data/Unemployment.xls', skip=6) # get rid of the first 6 rows 
shape=st_read('/Users/qianyi/Desktop/Data/tl_2019_us_county-1/tl_2019_us_county.shp')
```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center', include=FALSE}
# FIPS should be a 5-digits code, add 0 to the beginning
countypres$FIPS=ifelse(nchar(countypres$FIPS)==5, countypres$FIPS, paste('0',countypres$FIPS, sep=''))
countypres$FIPS=as.character(countypres$FIPS)
# calculate the proportion 
countypres['proportion']=countypres['candidatevotes']/countypres['totalvotes']

# group by
countypres=countypres %>% group_by(year, FIPS) %>% filter(year %in% c(2008,2012,2016)) %>% filter(party=='republican'|party=='democrat')

# convert year as character
countypres$year=as.character(countypres$year)

# only keep states of TX, CA, PA 
# countypres=countypres %>% filter(state_po=='TX'|state_po=='CA'|state_po=='PA') %>% select(c('year','state_po', 'FIPS', 'party', 'proportion'))

# save the cleaned dataset 
# write.csv(countypres, 'R_countypres_clean.csv')

```



```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# unemployment data set 
unemployment <- unemployment%>% select(c('FIPStxt', 'Stabr','Unemployment_rate_2008','Unemployment_rate_2012', 'Unemployment_rate_2016')) %>% rename(FIPS=FIPStxt)

# wide to long 
unemployment=unemployment %>% gather(key='key', value='value', -FIPS, -Stabr)

# split year and key into 2 different columns 
unemployment$year=unemployment$key %>% str_extract(.,'\\d+')
unemployment$key=unemployment$key %>% str_extract(.,'\\D+') %>% str_remove(., '_$') 
unemployment=unemployment%>% rename(unemployment_rate=value) %>% select(-c('key'))

# convert the unemployment rate into numerical format 
unemployment$unemployment_rate=as.numeric(unemployment$unemployment_rate)

# only keep states of TX, CA, PA 
# unemployment=unemployment %>% filter(Stabr=='TX'|Stabr=='CA'|Stabr=='PA')
# save the cleaned dataset 
# write.csv(unemployment, 'R_unemployment_clean.csv')

```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center',include=FALSE}
# python data cleaning part (Task 1)
library(reticulate)
py_install('pandas')
py_install('numpy')
```

```{python,include=FALSE}
import pandas as pd 
import numpy as np 
countypres=pd.read_csv("/Users/qianyi/Desktop/Data/countypres_2000-2016.csv")
### election data cleaning 
## (1) calculate the proportion 
countypres['proportion']=countypres['candidatevotes']/countypres['totalvotes']

## (2) filter years 
countypres=countypres[(countypres.year==2008)|(countypres.year==2012)|(countypres.year==2016)]

## (3) keep republican and democrat
countypres=countypres[(countypres.party=='republican')|(countypres.party=='democrat')]
countypres=countypres[['year','state_po', 'FIPS', 'party', 'proportion']]

## drop na 
countypres=countypres.dropna()
countypres['FIPS']=countypres['FIPS'].astype(int)
countypres['FIPS']=countypres['FIPS'].astype(str)

## (4) only keep TX, CA, PA states 
countypres=countypres[(countypres.state_po=='TX')|(countypres.state_po=='CA')|(countypres.state_po=='PA')]
# reindex
countypres=countypres.reset_index(drop=True)

## (5) fill FIPS digits 
# there are some code fips code have only 4 digits, add 0 at beginning  

for i in range(countypres.shape[0]):
    if len(countypres['FIPS'][i])==4:
        countypres['FIPS'][i]='0'+countypres['FIPS'][i]

## save the cleaned dataset 
#countypres.to_csv('python_contypres_clean.csv')    
```


```{python,include=FALSE}
unemployment=pd.read_excel("/Users/qianyi/Desktop/Data/Unemployment.xls", skiprows=6)
new_header = unemployment.iloc[0] #grab the first row for the header
unemployment = unemployment[1:] #take the data less the header row
unemployment.columns = new_header #set the header row as the df header
unemployment=unemployment[['FIPStxt', 'Stabr','Unemployment_rate_2008','Unemployment_rate_2012', 'Unemployment_rate_2016']]

# only keep data for TX, CA and PA 
unemployment=unemployment[(unemployment.Stabr=='TX')|(unemployment.Stabr=='CA')|(unemployment.Stabr=='PA')]

# wide to long 
unemployment=pd.wide_to_long(unemployment,stubnames='Unemployment_rate', 
                    i=['FIPStxt'], 
                    j='year', sep='_',suffix='\\d+')
                    
unemployment['id']=unemployment.index
unemployment=unemployment.reset_index(drop=True)
unemployment[['FIPS', 'year']] = pd.DataFrame(unemployment['id'].tolist(), index=unemployment.index)   
# drop the id column 
unemployment=unemployment.drop(columns=['id'])

## save the cleaned dataset 
#unemployment.to_csv('python_unemployment_clean.csv')
```





#### Draw choropleths with chosen party: democrat
```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center' ,include=FALSE}
#### Task 2 draw choropleths: chosen party: democrat
# load map data 
tx_map = shape %>% filter(STATEFP =='48') %>% rename('FIPS'='GEOID')
ca_map = shape %>% filter(STATEFP =='06') %>% rename('FIPS'='GEOID')
pa_map = shape %>% filter(STATEFP =='42') %>% rename('FIPS'='GEOID')


```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}

# State: TX Vote 
vote_tx_2008=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='TX') %>% filter(year=='2008') %>% filter(party=='democrat')
vote_tx_2012=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='TX') %>% filter(year=='2012') %>% filter(party=='democrat')
vote_tx_2016=countypres %>% select(c("year",  "FIPS","state_po","party", "proportion"))%>% filter(state_po=='TX') %>% filter(year=='2016')%>% filter(party=='democrat')

tx_2008 = tx_map %>% left_join(vote_tx_2008[,c('FIPS',"proportion")],by='FIPS') 
tx_2012 = tx_map %>% left_join(vote_tx_2012[,c('FIPS',"proportion")],by='FIPS')
tx_2016 = tx_map %>% left_join(vote_tx_2016[,c('FIPS',"proportion")],by='FIPS')

# vote map 
TX_2008 = ggplot(tx_2008) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2008 Vote proportion of Democrat of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

TX_2012 = ggplot(tx_2012) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2012 Vote proportion of Democrat of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

TX_2016 = ggplot(tx_2016) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2016 Vote proportion of Democrat of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

# State: TX unemployment 
rate_tx_2008=unemployment %>% filter(Stabr=='TX') %>% filter(year=='2008')
rate_tx_2012=unemployment %>% filter(Stabr=='TX') %>% filter(year=='2012')
rate_tx_2016=unemployment %>% filter(Stabr=='TX') %>% filter(year=='2016')

rate_tx_2008_map=tx_map %>% left_join(rate_tx_2008, by='FIPS')
rate_tx_2012_map=tx_map %>% left_join(rate_tx_2012, by='FIPS')
rate_tx_2016_map=tx_map %>% left_join(rate_tx_2016, by='FIPS')

# TX unemployment map 
rate_TX_2008 = ggplot(rate_tx_2008_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8, direction = -1)+labs(title='2008 Unemployment Rate of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_TX_2012 = ggplot(rate_tx_2012_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8, direction = -1)+labs(title='2012 Unemployment Rate of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_TX_2016 = ggplot(rate_tx_2016_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8, direction = -1)+labs(title='2016 Unemployment Rate of Texas')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
# State: CA Vote 
vote_ca_2008=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='CA') %>% filter(year=='2008') %>% filter(party=='democrat')
vote_ca_2012=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='CA') %>% filter(year=='2012') %>% filter(party=='democrat')
vote_ca_2016=countypres %>% select(c("year",  "FIPS","state_po","party", "proportion"))%>% filter(state_po=='CA') %>% filter(year=='2016')%>% filter(party=='democrat')

ca_2008 = ca_map %>% left_join(vote_ca_2008[,c('FIPS',"proportion")],by='FIPS') 
ca_2012 = ca_map %>% left_join(vote_ca_2012[,c('FIPS',"proportion")],by='FIPS')
ca_2016 = ca_map %>% left_join(vote_ca_2016[,c('FIPS',"proportion")],by='FIPS')

# vote map 
CA_2008 = ggplot(ca_2008) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2008 Vote proportion of Democrat of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

CA_2012 = ggplot(ca_2012) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2012 Vote proportion of Democrat of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

CA_2016 = ggplot(ca_2016) +geom_sf(aes(geometry=geometry,fill=proportion))+scale_fill_viridis(direction = -1)+labs(title='2016 Vote proportion of Democrat of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))


# State: CA unemployment 
rate_ca_2008=unemployment %>% filter(Stabr=='CA') %>% filter(year=='2008')
rate_ca_2012=unemployment %>% filter(Stabr=='CA') %>% filter(year=='2012')
rate_ca_2016=unemployment %>% filter(Stabr=='CA') %>% filter(year=='2016')

rate_ca_2008_map=ca_map %>% left_join(rate_ca_2008, by='FIPS')
rate_ca_2012_map=ca_map %>% left_join(rate_ca_2012, by='FIPS')
rate_ca_2016_map=ca_map %>% left_join(rate_ca_2016, by='FIPS')

# CA unemployment map 
rate_CA_2008 = ggplot(rate_ca_2008_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+labs(title='2008 Unemployment Rate of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_CA_2012 = ggplot(rate_ca_2012_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+labs(title='2012 Unemployment Rate of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_CA_2016 = ggplot(rate_ca_2016_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+labs(title='2016 Unemployment Rate of California')+xlab('Longitude')+ylab('Latitude')+theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

```


```{r,echo=FALSE, warning=FALSE, message=FALSE, fig.align='center'}
# fig1, fig.height = 30, fig.width = 25, fig.align = "center"
# State: PA Vote 
vote_pa_2008=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='PA') %>% filter(year=='2008') %>% filter(party=='democrat')
vote_pa_2012=countypres %>% select(c("year", "FIPS","state_po","party", "proportion"))%>% filter(state_po=='PA') %>% filter(year=='2012') %>% filter(party=='democrat')
vote_pa_2016=countypres %>% select(c("year",  "FIPS","state_po","party", "proportion"))%>% filter(state_po=='PA') %>% filter(year=='2016')%>% filter(party=='democrat')

pa_2008 = pa_map %>% left_join(vote_pa_2008[,c('FIPS',"proportion")],by='FIPS') 
pa_2012 = pa_map %>% left_join(vote_pa_2012[,c('FIPS',"proportion")],by='FIPS')
pa_2016 = pa_map %>% left_join(vote_pa_2016[,c('FIPS',"proportion")],by='FIPS')

# vote map 
PA_2008 = ggplot(pa_2008) +geom_sf(aes(geometry=geometry,fill=proportion))+
    scale_fill_viridis(direction = -1)+
    labs(title='2008 Vote proportion of Democrat of Pennsylvania', fill='proportion')+
    xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

PA_2012 = ggplot(pa_2012) +geom_sf(aes(geometry=geometry,fill=proportion))+
    scale_fill_viridis(direction = -1)+
    labs(title='2012 Vote proportion of Democrat of Pennsylvania', fill='proportion')+
    xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

PA_2016 = ggplot(pa_2016) +geom_sf(aes(geometry=geometry,fill=proportion))+
    scale_fill_viridis(direction = -1)+
    labs(title='2016 Vote proportion of Democrat of Pennsylvania', fill='proportion')+
    xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))


# State: PA unemployment 
rate_pa_2008=unemployment %>% filter(Stabr=='PA') %>% filter(year=='2008')
rate_pa_2012=unemployment %>% filter(Stabr=='PA') %>% filter(year=='2012')
rate_pa_2016=unemployment %>% filter(Stabr=='PA') %>% filter(year=='2016')

rate_pa_2008_map=pa_map %>% left_join(rate_pa_2008, by='FIPS')
rate_pa_2012_map=pa_map %>% left_join(rate_pa_2012, by='FIPS')
rate_pa_2016_map=pa_map %>% left_join(rate_pa_2016, by='FIPS')

# PA unemployment map 
rate_PA_2008 = ggplot(rate_pa_2008_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+
    labs(title='2008 Unemployment Rate of Pennsylvania', fill='unemployment Rate(%)')+xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_PA_2012 = ggplot(rate_pa_2012_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+
    labs(title='2012 Unemployment Rate of Pennsylvania', fill='unemployment Rate(%)')+xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))

rate_PA_2016 = ggplot(rate_pa_2016_map)+geom_sf(aes(geometry=geometry,fill = unemployment_rate))+
        scale_fill_viridis_c(name='unemployment rate (%)',option = "plasma", alpha = .8,direction = -1)+
    labs(title='2016 Unemployment Rate of Pennsylvania', fill='unemployment Rate(%)')+xlab('Longitude')+ylab('Latitude')+
    theme(plot.title = element_text(color = "black", size = 24, vjust = 1,hjust = 0.5, face="bold"),
          legend.title = element_text(color = "black", size = 18),
          legend.text = element_text(color = "black", size = 18), 
          legend.position="right",
          panel.spacing.x=unit(5, "lines"), aspect.ratio =1,
          axis.text=element_text(size=14),
          axis.title=element_text(size=16,face="bold"))
```


#### Grographical plots for TX 
```{r, fig.height = 30, fig.width = 25,echo=FALSE, warning=FALSE, message=FALSE, fig.align = "center"}
ggarrange(TX_2008, rate_TX_2008,TX_2012, rate_TX_2012,TX_2016, rate_TX_2016,ncol = 2, nrow=3, align = 'hv', widths = c(7,7,7,7,7,7))
```

#### Grographical plots for CA
```{r, fig.height = 30, fig.width = 25,echo=FALSE, warning=FALSE, message=FALSE, fig.align = "center"}
ggarrange(CA_2008, rate_CA_2008,CA_2012, rate_CA_2012,CA_2016, rate_CA_2016,ncol = 2, nrow=3, align = 'hv', widths = c(7,7,7,7,7,7))
```

#### Grographical plots for PA
```{r, fig.height = 30, fig.width = 25,echo=FALSE, warning=FALSE, message=FALSE, fig.align = "center"}
ggarrange(PA_2008, rate_PA_2008,PA_2012, rate_PA_2012,PA_2016, rate_PA_2016,ncol = 2, nrow=3, align = 'hv', widths = c(7,7,7,7,7,7))
```

### Discussion of the Visualization 

For Texas, the counties with higher democrat vote proportions had relatively higher unemployment rates during the year of 2008, 2012 and 2016; For California, the counties in the middle and very south areas had relatively higher unemployment rate, but overall, the counties with higher democrat vote proportions had relatively lower unemployment rates;For Pennsylvania, the counties with higher democrat vote proportions had relatively higher unemployment rates during the year of 2008, 2012 but not for the year of 2016.
