---
title: "Visualization Project: UFO sights in USA"
output: flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(base)
library(lubridate)
library(tidyverse)
library(anytime) 
library(tibble)
library(ggplot2)
library(ggrepel)
library(igraph)
library(wordcloud)
library(tidytext)
library(janeaustenr)
library(widyr)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(quanteda)

# data cleaning 
ufo=read.csv('ufo_sighting_data.csv')
# keep records that in US only 
ufo=ufo[ufo$country=='us', ]

# delete described_duration_of_encounter column, because all the encounter time was converted to length_of_encounter_seconds 
# delete date_documented column because all we need is date of ufo observed 
ufo=ufo %>% select(-c('described_duration_of_encounter','date_documented'))

# convert state abbreviation to upper case 
ufo$state.province= toupper(ufo$state.province) 

# create time and date column 
ufo<- ufo %>% add_column(date = NA, .after="Date_time")
ufo<- ufo %>% add_column(time = NA, .after="date")
ufo<- ufo %>% add_column(year = NA, .after="time")
ufo<- ufo %>% add_column(month = NA, .after="year")
ufo<- ufo %>% add_column(day = NA, .after="month")
ufo<- ufo %>% add_column(hour = NA, .after="day")
ufo<- ufo %>% add_column(weekdays = NA, .after="hour")

# split date and time into different columns
ufo$date=sapply(ufo$Date_time, function(x) as.character(strsplit(x, ' ')[[1]][1]))
ufo$time=sapply(ufo$Date_time, function(x) as.character(strsplit(x, ' ')[[1]][2]))

# convert date to year, month, day separately 
ufo$month= sapply(ufo$date, function(x) as.numeric(strsplit(x, '/')[[1]][1]))
ufo$day= sapply(ufo$date, function(x) as.numeric(strsplit(x, '/')[[1]][2]))
ufo$year= sapply(ufo$date, function(x) as.numeric(strsplit(x, '/')[[1]][3]))

# convert date to weekdays 
ufo$weekdays=weekdays(as.Date(ufo$date,'%m/%d/%Y'))

# convert time to hour 
ufo$hour= sapply(ufo$time, function(x) as.numeric(strsplit(x, ':')[[1]][1]))

# convert latitude and longitude into numeric value 
ufo$latitude=as.numeric(ufo$latitude)
ufo$longitude=as.numeric(ufo$longitude)

# drop na value and empty value
# reference: https://stackoverflow.com/questions/9126840/delete-rows-with-blank-values-in-one-particular-column
ufo=ufo %>%na_if('') %>%na.omit

```

About
=========================================

Column
-----------------------------------------
Dataset Introduction: 

This dataset included 80000+ records about UFO observations in US states or Canada from year 1949 to year 2014. It has longitude, latitude data (geographical), and UFO observer description (text) as well as specific year/month/date data (time series). The majority records are about UFO inside the United States. In this project, I focused more on the records within the US.

Here are the specific column descriptions:

* Date_time - standardized date and time of sighting

* city - location of UFO sighting

* state/province - the US state or Canadian province, appears blank for other locations

* country - Country of UFO sighting

* UFO_shape - a one word description of the "spacecraft"

* length_of_encounter_seconds - standardized to seconds, length of the observation of the UFO

* described_duration _of_encounter - raw description of the length of the encounter 

* description - text description of the UFO encounter

* date_documented - when was the UFO sighting reported

* latitude - latitude

* longitude - longitude


Dataset Link: https://www.kaggle.com/camnugent/ufo-sightings-around-the-world


Visualization Overview: 
In this project, I created pie chart, histogram, bar chart, violin plot, heatmap, geographical map, network, time series plot, text wordcloud, and text relative word frequency plot. Through these visualizations, we could generate some insights about UFOs: 

* The light, triangle, circle, and fireball shape are the top 4 shapes among all the UFO recorded. 

* According to observers description, the common features of these frequently appeared shape UFOs are red color and light. 

* Flash and chevron shapes have relatively shorter observed time duration while delta and diamond shapes have relatively longer observed time duration.

* UFOs are more likely to appear on Weekends from June through November. 

* States that are near US coastline have more UFO records. The great California area and the great New York area have more UFO records than other states in US.

* California seems to have a large amount of light shape UFOs and relatively rich number of circle shape UFOs. Taxes and Washington states also have rich light shape UFOs.

* The amount of UFOs increased a lot since year 1997. Since January 2020, the amount of UFO records has an increasing trend with growing fluctuation and variation. 



Exploratory Data Analysis {.storyboard}
=========================================

### EDA 1: Pie Chart: --During 1910 to 2014, the most frequently appeared shapes are: light, triangle, circle, and fireball. Some shapes are extremely rare, for example, hexagon, flare, crescent, and pyramid.

```{r pie_chart,fig.height = 10, fig.width = 20, fig.align = "center" }
df1=ufo %>% select(c("UFO_shape")) %>% group_by(UFO_shape) %>% count() %>% rename(shape_count=n)
df1=df1[with(df1,order(shape_count,decreasing = TRUE)), ]
# pie chart 
# reference: https://www.r-graph-gallery.com/piechart-ggplot2.html
# reference: https://stackoverflow.com/questions/42654132/r-pie-chart-labels-overlap-ggplot2

df1 <- df1 %>% 
  arrange(desc(UFO_shape)) %>%
  mutate(prop = shape_count / sum(df1$shape_count) *100) # calculate the proportion 

# prepare for the annotation labels
my_labels <- tibble(x.breaks = seq(1, 1.5, length.out =28),
                    y.breaks =  cumsum(df1$shape_count)-df1$shape_count/2,
                    labels = paste(df1$UFO_shape, paste0(round(df1$prop,2), "%"), sep='\n'),
                    UFO_shape = df1$UFO_shape)

ggplot(df1, aes(x = 1, y = shape_count, fill = UFO_shape)) +
  labs(title="UFO shapes from 1910 to 2014", size=15) +
  geom_bar(stat="identity", color='black') + 
  coord_polar(theta='y') + 
  guides(fill=guide_legend(title="UFO Shapes", override.aes=list(colour=NA)))+
  scale_fill_hue(c=45, l=70)+ # Setting luminance and saturation (chromaticity)
  theme_void()+ # remove the default theme 
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=20))+
  geom_label_repel(data = my_labels, aes(x = x.breaks, y = y.breaks, label = labels, fill = UFO_shape),label.padding = unit(0.13, "lines"),size = 2,show.legend = FALSE,inherit.aes = FALSE) # make sure the annotation not overlap each other 
```



### EDA 2: Histogram of UFO Time Duration--After the log operation, the time duration data are almost normally distributed.  

```{r hist,fig.height = 10, fig.width = 18, fig.align = "center" }
par(mfrow=c(1,2))
df2=ufo %>% select(c("UFO_shape","length_of_encounter_seconds")) 
df2$length_of_encounter_seconds=as.numeric(df2$length_of_encounter_seconds)
hist(df2$length_of_encounter_seconds,breaks=30, main="Seconds among UFOs (before log)", xlab="seconds", ylab="Frequency", col="lightpink")

# since time have very large range, log value may better
# convert seconds to log seconds 
df2$length_of_encounter_seconds=log(df2$length_of_encounter_seconds)
df2=df2 %>% rename(log_seconds=length_of_encounter_seconds)
hist(df2$log_seconds, main="Log seconds among UFOs", xlab="log seconds", ylab="Frequency", col="lightblue")
```


### EDA 3: Violin Plot: --Flash and chevron shapes have relatively shorter observed time duration while delta and diamond shapes have relatively longer observed time duration.

```{r fig_violin, fig.height = 10, fig.width = 30, fig.align = "center"}
ggplot(df2, aes(x=UFO_shape, y=log_seconds, fill=UFO_shape)) + 
  geom_violin(trim=FALSE)+
  scale_fill_hue(c=45, l=70)+
  geom_boxplot(width=0.2)+
   labs(title="UFO Log Seconds Among Different Shapes")+theme_minimal()+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=40), 
        axis.text.x = element_text(color = "black", size = 15, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 15, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size = 20, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size = 20, hjust = 0.5, vjust = 0.5, face = "plain"),
        legend.position = "none")+
  xlab('UFO Shapes')+
  ylab('Log Seconds')
```


### EDA 4: Bar Chart: --The amount of UFO increased a lot since year 1997 

```{r fig_bar_count, fig.height = 5, fig.width = 10, fig.align = "center"}
df3=ufo %>% select(c('year', 'UFO_shape'))
ggplot(df3, aes(year, fill="lightorgange"))+geom_bar()+
  scale_fill_hue(c=45, l=70)+
  labs(title="UFO Count from 1910 to 2014")+
  xlab('Year')+
  ylab('Yearly Count of UFOs')+theme_minimal()+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=15), legend.position = "none",
        axis.text.x = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"))

```


### EDA 5：Bar Chart: --Dive into States, the top 4 states with UFO recourds are CA, FL, WA, TX 
```{r fig_bar_state, fig.height = 7, fig.width = 7, fig.align = "center"}
df4=ufo %>% select(c("state.province")) %>% group_by(state.province) %>% count() %>% rename(state_count=n)
df4=df4[with(df4,order(state_count,decreasing = TRUE)), ]
ggplot(data = df4, mapping = aes(x = reorder(state.province, state_count), state_count)) + 
  geom_bar(aes(fill = state_count),stat = "identity") + coord_flip()+
  scale_fill_gradient(low = "lightyellow", high = "darkgreen", na.value = NA)+
  labs(title="UFO Counts in Each States")+theme_minimal()+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=20), 
        axis.text.x = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size = 12, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size = 12, hjust = 0.5, vjust = 0.5, face = "plain"),
        legend.position = "none")+
  xlab('State Abbreviation')+
  ylab('UFO Count')
# the top 4 states are CA, FL, WA, TX 

```


Heatmap {.storyboard}
=========================================

### Heatmap for Year 1990s: UFOs are more frequently appeared from June to November, with relatively high frequency on Tuesday 

```{r fig_heat1990, fig.height = 6, fig.width = 12, fig.align = "center"}
# for year 1990-1999
df1990=ufo %>% select(c("year", "month", "weekdays")) %>% filter(year>=1990 & year<=1999)
df1990=df1990 %>% group_by(month, weekdays) %>% count() %>% rename(count=n)
df1990$month=as.factor(df1990$month)
df1990$weekdays=as.factor(df1990$weekdays)
df1990$weekdays <- factor(df1990$weekdays, levels= c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday","Saturday","Sunday"))

ggplot(df1990, aes(month, weekdays, fill= count)) +
  geom_tile()+scale_fill_gradient(low = "lightyellow", high = "darkred", na.value = NA)+
   labs(title="Heatmap of Weekdays and Month for 1990s")+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=15), 
        axis.text.x = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"))+
  xlab('Month')+
  ylab('Weekdays')
```

### Heatmap for Year 2000s: UFOs are more frequently appeared from June to November, with high frequency during weekends 

```{r fig_heat2000, fig.height = 6, fig.width = 12, fig.align = "center"}
# for year 2000-2009
df2000=ufo %>% select(c("year", "month", "weekdays")) %>% filter(year>=2000 & year<=2009)
df2000=df2000 %>% group_by(month, weekdays) %>% count() %>% rename(count=n)
df2000$month=as.factor(df2000$month)
df2000$weekdays=as.factor(df2000$weekdays)
df2000$weekdays <- factor(df2000$weekdays, levels= c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday","Saturday","Sunday"))

ggplot(df2000, aes(month, weekdays, fill= count)) +
  geom_tile()+scale_fill_gradient(low = "lightyellow", high = "darkred", na.value = NA)+
   labs(title="Heatmap of Weekdays and Month for 2000s")+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=15), 
        axis.text.x = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"))+
  xlab('Month')+
  ylab('Weekdays')
```

### Heatmap for Year 2010s: UFOs are more frequently appeared from June to September, with high frequency on  Saturday  

```{r fig_heat2010, fig.height = 6, fig.width = 12, fig.align = "center"}
# for year 2010-2019
df2010=ufo %>% select(c("year", "month", "weekdays")) %>% filter(year>=2010 & year<=2019)
df2010=df2010 %>% group_by(month, weekdays) %>% count() %>% rename(count=n)
df2010$month=as.factor(df2010$month)
df2010$weekdays=as.factor(df2010$weekdays)
df2010$weekdays <- factor(df2010$weekdays, levels= c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday","Saturday","Sunday"))

ggplot(df2010, aes(month, weekdays, fill= count)) +
  geom_tile()+scale_fill_gradient(low = "lightyellow", high = "darkred", na.value = NA)+
   labs(title="Heatmap of Weekdays and Month for 2010s")+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=15), 
        axis.text.x = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"))+
  xlab('Month')+
  ylab('Weekdays')
```


Geographical Visualization {.storyboard}
=========================================

### Geographical Map:-- States that are near US coastline have more UFO records. The great California area and the great New York area have more UFO records than other states in US.
```{r fig_geo, fig.height = 9, fig.width = 15, fig.align = "center"}
MainStates <- map_data("state")
# prepare data and join with the map 
df6=ufo %>% select(c("state.province")) %>% group_by(state.province) %>% count() %>% rename(state_count=n, region=state.province)
# remove HI, PR, and AK 
df6=df6 %>% filter(region!='HI' & region!='AK' & region!='PR')

# convert state abbreviation into lowercase full state name 
# reference: https://favorableoutcomes.wordpress.com/2012/10/19/create-an-r-function-to-convert-state-codes-to-full-state-name/
#'x' is the column of a data.frame that holds 2 digit state codes
stateFromLower <-function(x) {
  #read 52 state codes into local variable [includes DC (Washington D.C. and PR (Puerto Rico)]
  st.codes<-data.frame(
                      state=as.factor(c("AK", "AL", "AR", "AZ", "CA", "CO", "CT", "DC", "DE", "FL", "GA",
                                         "HI", "IA", "ID", "IL", "IN", "KS", "KY", "LA", "MA", "MD", "ME",
                                         "MI", "MN", "MO", "MS",  "MT", "NC", "ND", "NE", "NH", "NJ", "NM",
                                         "NV", "NY", "OH", "OK", "OR", "PA", "PR", "RI", "SC", "SD", "TN",
                                         "TX", "UT", "VA", "VT", "WA", "WI", "WV", "WY")),
                      full=as.factor(c("alaska","alabama","arkansas","arizona","california","colorado",
                                       "connecticut","district of columbia","delaware","florida","georgia",
                                       "hawaii","iowa","idaho","illinois","indiana","kansas","kentucky",
                                       "louisiana","massachusetts","maryland","maine","michigan","minnesota",
                                       "missouri","mississippi","montana","north carolina","north dakota",
                                       "nebraska","new hampshire","new jersey","new mexico","nevada",
                                       "new york","ohio","oklahoma","oregon","pennsylvania","puerto rico",
                                       "rhode island","south carolina","south dakota","tennessee","texas",
                                       "utah","virginia","vermont","washington","wisconsin",
                                       "west virginia","wyoming"))
                       )
     #create an nx1 data.frame of state codes from source column
  st.x<-data.frame(state=x)
     #match source codes with codes from 'st.codes' local variable and use to return the full state name
  refac.x<-st.codes$full[match(st.x$state,st.codes$state)]
     #return the full state names in the same order in which they appeared in the original source
  return(refac.x)
}
df6$region<-stateFromLower(df6$region)

# merge dataset 
MergedStates <- inner_join(MainStates, df6, by = "region")

# data preprocessing for geompoint 
geompoint =ufo %>% select(c("state.province", "latitude", "longitude")) %>% rename(region=state.province) %>% filter(region!='HI' & region!='AK' & region!='PR')

# reference: https://remiller1450.github.io/s230s19/Intro_maps.html
ggplot()+ geom_polygon(data=MergedStates, aes(x=long, y=lat, group=group, fill = state_count), color="white", size = 0.2)+
  scale_fill_continuous(name="UFO Records Count", 
                        low = "lightblue", high = "darkblue",
                         na.value = "grey50") +
  geom_point(data=filter(geompoint),aes(x=longitude,y=latitude),alpha=.5,size=.5, color="darkred")+
  labs(title="UFO Records in US Main States")+
   xlab('Longitude')+
  ylab('Latitude')+theme_minimal()+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=20), 
        axis.text.x = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =15, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =15, hjust = 0.5, vjust = 0.5, face = "plain"))

```

Network {.storyboard}
=========================================

### Shape and States Network:-- California seems to have a large amount of light shape UFOs and relatively rich number of circle shape UFOs. Taxes and Washington states also have rich light shape UFOs.

```{r fig_network, fig.height = 10, fig.width = 10, fig.align = "center"}
df7=ufo %>% select(c("UFO_shape","state.province"))
# filter out states that have less than 200 count of UFO records 
remain_states=df7 %>% group_by(state.province) %>% count() %>% filter(n>200) %>% select(c("state.province"))
# filter out shapes that have less than 200 count of UFO records 
remain_shape=df7 %>% group_by(UFO_shape) %>% count() %>% filter(n>200)%>% select(c("UFO_shape"))
# combine dataset 
df7=ufo %>% select(c("UFO_shape","state.province")) %>% inner_join(remain_states, by="state.province") %>% inner_join(remain_shape,by = "UFO_shape") %>% drop_na()

df7=df7%>% group_by(state.province, UFO_shape) %>% count() %>% rename(count=n, target=state.province, source=UFO_shape)

nodes <- data.frame(
    name=c(as.vector(unique(df7$target)), as.vector(unique(df7$source))),
    type=c(rep("state",46), rep("shape",20))
    )

network <- graph_from_data_frame(d=df7, vertices=nodes,directed=F) 

# Create a vector of color
coul=c("tomato", "gold")
my_color <- coul[as.numeric(as.factor(V(network)$type))]

plot(network,edge.width=df7$count/250, vertex.size=5, vertex.color=my_color,vertex.frame.color="#ffffff", vertex.label.color="black",main="Network of Shape and States")
```


Time Series {.storyboard}
=========================================

### UFO Time Series:-- Since January 2020, the amount of UFO records has an increasing trend with growing fluctuation and variation 

```{r fig_time_series, fig.height = 10, fig.width = 20, fig.align = "center"}
df8=ufo %>% select(c("date","year","month","day"))
df8$DATE=paste0(df8$year,'-',df8$month,'-',df8$day)
df8$DATE=as.Date(df8$DATE)
df8=df8 %>% group_by(DATE) %>% count() %>% rename(UFO_Count=n)
# Before year 1990, the UFO count are very limited, I will focus on the time series after 1990  
df8=df8 %>% filter(DATE>='1990-01-01')
# range(df8$DATE)

ggplot(df8, aes(x=DATE, y=UFO_Count)) +
  geom_line(color="#69b3a2") + 
  geom_smooth(method='loess', size=1, se=F, span=0.05, formula = y~x)+
  scale_x_date(date_labels = "%Y %b %d")+
  labs(title="UFO Time Series from 1990 to 2014")+
   xlab('Date')+
  ylab('UFO Count')+theme_minimal()+
  theme(plot.title = element_text(face = "bold",hjust = 0.5, size=20), 
        axis.text.x = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =15, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =15, hjust = 0.5, vjust = 0.5, face = "plain"))


```

Text Visualization {.storyboard}
=========================================

### UFO Description Wordcloud: --Most descriptions are about light, color and moving speed

```{r fig_wordcloud}
# reference http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know
df9=ufo %>% select(c("description"))
text<- paste(df9$description,collapse = " ")  #All titles into one

# Load the data as a corpus
docs <- Corpus(VectorSource(text))

# text data cleaning
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\|")

# Convert the text to lower case
docs <- tm_map(docs, content_transformer(tolower))
# Remove numbers
docs <- tm_map(docs, removeNumbers)
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
# Text stemming
docs <- tm_map(docs, stemDocument)


# plot the word frequency 
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

set.seed(213)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "PuOr"))
```


### Relative Word Frequency by Top 4 Shape:--For the top 4 shapes, their common features are red color and lights 
```{r fig_rwf}
# reference: https://quanteda.io/articles/pkgdown/examples/plotting.html
df10=ufo %>% select(c('description', 'UFO_shape')) %>% filter(UFO_shape=='light'|UFO_shape=='triangle'|UFO_shape=='circle'|UFO_shape=='fireball')

# light 
light_corpus=df10 %>% filter(UFO_shape=='light')
light_corpus=paste(light_corpus$description,collapse = " ")  #combine all discriptions into one 
light_corpus=gsub("[^a-zA-Z]", " ", light_corpus) # remove numbers and special charecter 
light_corpus=light_corpus %>% dfm(stem = TRUE,remove = stopwords("english"), remove_punct = TRUE) %>% dfm_weight(scheme = "prop")
light_freq_weight <- textstat_frequency(light_corpus, n = 15, groups = "light")

# triangle 
triangle_corpus=df10 %>% filter(UFO_shape=='triangle')
triangle_corpus=paste(triangle_corpus$description,collapse = " ")  #combine all discriptions into one 
triangle_corpus=gsub("[^a-zA-Z]", " ", triangle_corpus)# remove numbers and special charecter 
triangle_corpus=triangle_corpus %>% dfm(stem = TRUE,remove = stopwords("english"), remove_punct = TRUE) %>% dfm_weight(scheme = "prop")
triangle_freq_weight <- textstat_frequency(triangle_corpus, n = 15, groups = "triangle")

# circle
circle_corpus=df10 %>% filter(UFO_shape=='circle')
circle_corpus=paste(circle_corpus$description,collapse = " ") #combine all discriptions into one 
circle_corpus=gsub("[^a-zA-Z]", " ", circle_corpus)# remove numbers and special charecter 
circle_corpus=circle_corpus %>% dfm(stem = TRUE,remove = stopwords("english"), remove_punct = TRUE) %>% dfm_weight(scheme = "prop")
circle_freq_weight <- textstat_frequency(circle_corpus, n = 15, groups = "circle")

# fireball
fireball_corpus=df10 %>% filter(UFO_shape=='fireball')
fireball_corpus=paste(fireball_corpus$description,collapse = " ")  #combine all discriptions into one 
fireball_corpus=gsub("[^a-zA-Z]", " ", fireball_corpus)# remove numbers and special charecter 
fireball_corpus=fireball_corpus %>% dfm(stem = TRUE,remove = stopwords("english"), remove_punct = TRUE) %>% dfm_weight(scheme = "prop")
fireball_freq_weight <- textstat_frequency(fireball_corpus, n = 15, groups = "fireball")

# concatenate these data 
freq_data=rbind(light_freq_weight, triangle_freq_weight,circle_freq_weight , fireball_freq_weight)


ggplot(data = freq_data, aes(x = nrow(freq_data):1, y = frequency, color=group)) +
     geom_point() +
     facet_wrap(~ group, scales = "free") +
     coord_flip() +
     scale_x_continuous(breaks = nrow(freq_data):1,labels = freq_data$feature) +
     labs(x = NULL, y = "Relative Frequency", title='Relative Word Frequency for Top 4 Shapes')+
  theme_bw()+theme(panel.border = element_rect(color = "darkgrey", size = 2),
                   plot.title = element_text(face = "bold",hjust = 0.5, size=15), 
                   legend.title = element_blank(),
        axis.text.x = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.text.y = element_text(color = "black", size = 7, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.x = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"),
        axis.title.y = element_text(color = "black", size =10, hjust = 0.5, vjust = 0.5, face = "plain"))


```









